Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-15 paper/main.tex
fix sub*3

\author{\IEEEauthorblockN{1\textsuperscript{st} Zhen Chen}
\IEEEauthorblockA{\textit{Faculty of Computing and Mathematical Sciences} \\
\textit{The University of Waikato}\\
Beijing, China \\
1561010}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Huajie Xu}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Shengzhu Wang}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Wenjie Tong}
\IEEEauthorblockA{\textit{Faculty of Computer Sciences} \\
\textit{The University of Waikato}\\
Guizhou, China \\
benji.tong1117@gmail.com}
\and
\IEEEauthorblockN{5\textsuperscript{th} SiXiang Xiong}
\IEEEauthorblockA{\textit{Faculty of Computer Sciences} \\
\textit{The University of Waikato}\\
Wuhan, China \\
1591686 sixianglearners3@gmail.com}
}

@@

\subsection{Frontend construction}

\subsubsection{NVM}

\subsubsection{NPM}

\subsubsection{Native Vue or Webpack}

\subsubsection{Vue cli}

"A simple CLI for scaffolding Vue.js projects" \cite{Introduc89:online}. With it, user can pull template from vuejs-templates and generate 
the basic webpack \+ Vue project.

\subsection{Frontend function}

\subsubsection{Third party login}

\subsubsection{Data visualization}

For three specific research-targeting areas, the data format is just like Fig.~\ref{dffg}. It is an array in which 
each element shows lots of details of one section of COG file at a particular time point. Because each time the section, also showed 
as “window” in the image, is different from each other, so directly comparing “radiance” of each element is meaningless. To show the 
level of night lights of different area, “radiance” divided by “pixels” is more valuable since it has nothing to do with the size of 
“window”.

@@

>>>>

\author{\IEEEauthorblockN{1\textsuperscript{st} Zhen Chen}
\IEEEauthorblockA{\textit{Faculty of Computing and Mathematical Sciences} \\
\textit{The University of Waikato}\\
Beijing, China \\
1561010}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Huajie Xu}
\IEEEauthorblockA{\textit{Faculty of Computing and Mathematical Sciences} \\
\textit{The University of Waikato}\\
Hefei, China \\
1580014}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Shengzhu Wang}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Wenjie Tong}
\IEEEauthorblockA{\textit{Faculty of Computer Sciences} \\
\textit{The University of Waikato}\\
Guizhou, China \\
benji.tong1117@gmail.com}
\and
\IEEEauthorblockN{5\textsuperscript{th} SiXiang Xiong}
\IEEEauthorblockA{\textit{Faculty of Computer Sciences} \\
\textit{The University of Waikato}\\
Wuhan, China \\
1591686 sixianglearners3@gmail.com}
}

@@

@@

\subsubsection{Frontend construction}

\paragraph{NVM}

\paragraph{NPM}

\paragraph{Native Vue or Webpack}

\paragraph{Vue cli}

"A simple CLI for scaffolding Vue.js \\projects" \cite{Introduc89:online}. With it, user can pull template from vuejs-templates and generate 
the basic webpack \+ Vue project.

\subsubsection{Frontend function}

\paragraph{Third party login}

\paragraph{Data visualization}

For three specific research-\\ targeting areas, the data format is just like Fig.~\ref{dffg}. It is an array in which 
each element shows lots of details of one section of COG file at a particular time point. Because each time the section, also showed 
as “window” in the image, is different from each other, so directly comparing “radiance” of each element is meaningless. To show the 
level of night lights of different area, “radiance” divided by “pixels” is more valuable since it has nothing to do with the size of 
“window”.
